Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-01 linear_adia.tex
merge with youdin's update

\subsection{An upper limit to the cooling time}\label{iso_vsi_beta_crit}
Here we estimate the maximum thermal relaxation timescale 
$\beta_c$ that allows growth the VSI.  In Appendix \ref{disp_neut_limit}
we derive the following relation between $\beta_c$ and the wave frequency,
\hat{\omega}_c$  at marginal stability to the VSI

%Our starting point is Eq. \ref{relax_cond1}---\ref{relax_cond2} which
%approximates the dispersion relation Eq. \ref{relax_disp} assuming marginal
%stability and $\khat^2\gg 1$. We consider $M=0$ (the 
%fundamental mode) or  $M=O(1)$ and low frequency $|\hat{\omega}|\ll
%1$ such that $|\hat{\omega}\khat|$ is $O(1)$. We 
%also assume $|q|$ and $\beta$ are $O(1)$ or smaller. 
%
%For a thin disk
%($h \ll 1$) we have 
\begin{subequations}\begin{align}
 \left(\hat{\omega}\khat\right)^4  = &  \left[1 +
    \gamma\beta^2\left(1-\gamma\right)(1+2M)^2\right]\left(\hat{\omega}\khat\right)^2 \label{relax_cond_simp1}\\ 
 &+ M(M+1)\left(1-h^2q^2\khat^2\right)
    , \notag \\
   \left(\hat{\omega}\khat\right)^2 = & \frac{\beta}{h q} (\gamma-1)(1+2M)^2
   \left(\hat{\omega}\khat\right) \label{relax_cond_simp2}\\
   $- 2M(M+1) , \notag
\end{align}\end{subequations}
These equations hold for $\beta_c \ll 1$ and $\hat{k} \sim 1/|\

>>>>

\subsection{An upper limit to the cooling time}\label{iso_vsi_beta_crit}
Here we estimate the maximum thermal relaxation timescale 
$\beta_c$ that allows growth the VSI.  In Appendix \ref{disp_neut_limit}
we derive the following relation between $\beta_c$ and the wave frequency,
$\hat{\omega}_c$  at marginal stability to the VSI

%Our starting point is Eq. \ref{relax_cond1}---\ref{relax_cond2} which
%approximates the dispersion relation Eq. \ref{relax_disp} assuming marginal
%stability and $\khat^2\gg 1$. We consider $M=0$ (the 
%fundamental mode) or  $M=O(1)$ and low frequency $|\hat{\omega}|\ll
%1$ such that $|\hat{\omega}\khat|$ is $O(1)$. We 
%also assume $|q|$ and $\beta$ are $O(1)$ or smaller. 
%
%For a thin disk
%($h \ll 1$) we have 
\begin{subequations}\begin{align}
 \left(\hat{\omega}\khat\right)^4  = &  \left[1 +
    \gamma\beta^2\left(1-\gamma\right)(1+2M)^2\right]\left(\hat{\omega}\khat\right)^2 \label{relax_cond_simp1}\\  
  &+ M(M+1)\left(1-h^2q^2\khat^2\right)
   , \notag \\
   \left(\hat{\omega}\khat\right)^2 = & \frac{\beta}{h q} (\gamma-1)(1+2M)^2
   \left(\hat{\omega}\khat\right)  
    - 2M(M+1).\label{relax_cond_simp2} %\notag 
\end{align}
\end{subequations}
These equations hold for $\beta_c \ll 1$ and $\hat{k} \gg1 $
